The problem and promise of scale in multilayer networks

### 2020-01-24 paper/manuscript.Rmd
temp scale
temp scale2

Varying length of time window (used to define seasons). From 75 to 150 right now. Fixed start julian day for winter is day 1 and for summer is 215. Network layers for winter and summer are calculated for each window length.

1. time window position
Varying position of time window (used to define seasons). Fixed length at 75. Window positions starting at 1, to + 75. So 1-75 is first iteration for winter and 75-150 is second iteration for "winter". Same for summer, starting at 215. Network layers for each season are constructed.

>>>>

Varying length of time window (used to define seasons). Starting with a window of day 1-40 and using a moving window to go to day 1-100. Fixed start julian day for winter is day 1 and for summer is 215. Network layers for winter and summer are calculated for each window length.

1. time window position
Varying position of time window (used to define seasons). Fixed length at 48 Window positions starting at 1, to + 48 So 1-48 is first iteration for winter and 48-96 is second iteration for "winter". Same for summer, starting at 215. Network layers for each season are constructed.
